Towards Reliable Machine Learning Deployments in the Cloud

### 2023-12-13 paper.tex
Updates from Overleaf

\title{Towards Reliable Machine Learning Deployments in the Cloud}
% \thanks{Identify applicable funding agency here. If none, delete this.}
\author{\IEEEauthorblockN{1\textsuperscript{st} Charles Meyers}
\IEEEauthorblockA{\textit{dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
cmeyers@cs.umu.se}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Mohammad Reza}
\IEEEauthorblockA{\textit{dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
fake@fake.se}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Tommy Löfstedt}
\IEEEauthorblockA{\textit{dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
tommmy@cs.umu.se}
\and
\IEEEauthorblockN{4\textsuperscript{th} Erik Elmroth}
\IEEEauthorblockA{\textit{dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
elmroth@cs.umu.se}
}

@@

\begin{abstract}
Considering the growing prominence of production-level AI and the threat of adversarial attacks that can poison a machine learning model against a certain label, evade classification, or reveal sensitive data about the model and training data to an attacker, adversaries pose fundamental problems to machine learning systems. Prior research has noted the need to extend beyond the normal train-test split paradigm for evaluating models due of the ease with which one can generally find adversarial counterexamples. Additionally, testing model changes likely means deploying the models to a car, medical imaging device, or drone to see how it affects performance, making un-tested changes a public problem. Furthermore, the relationship between model learning rate, batch size, training time, convergence time, and deployment cost is highly complex. So, instead of this train-test split methodology, we propose using accelerated failure time models to measure the effect of hardware choice, batch size, number of epochs, and learning rate by using adversarial attacks to induce failures on a reference model architecture. We evaluate several GPU types and use Tree Parzen Estimator to maximize model robustness and minimize model run-time simultaneously. In this way, we can evaluate our model and optimize it in a single step, which provides a precise way to not only measure the effect of different hardware deployments but also of the model parameters. Using this technique, we demonstrate that newer, more-powerful hardware does decrease the training time, but with a monetary and power cost that far outpaces the marginal gains in accuracy.
\end{abstract}

@@

\section{Introduction}
\subsection{Motivations}
\begin{itemize}
    % \item \textbf{BIG} Data is the trend
    % \item Costs are astronomical
    \item Prevailing regulatory framework is clear about the robustness requirements, documented software changes, and explainable processes.
    \item Other work relies on unreliable test/train split methodology
    \item Which means that cars, medical equipment is tested in the wild
\end{itemize}

Recently, artificial intelligence using neural networks has become a popular way to classify large amounts of data-- with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}. However, neural networks need huge amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, yielding increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}. Furthermore, popular models like general purpose transformer (GPT)\cite{floridi2020gpt} or ResNet~\cite{resnet} have hundreds of millions or billions of parameters, requiring equally large training datasets. Media reports place the cost of training a large language model somewhere between 4 and 63 million dollars~\cite{}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system. Luckily, Facebook's large language model, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}. Immediately, an open-sourced clone was created, which itself spawned hundreds of offshoot projects~\cite{openllama}. The newest version of this open-source LLM is able to outperform the commercially available GPT-3.5 model with a fraction of the parameters (13 Billion), small enough to run on a laptop without a graphics processing unit (GPU)~\cite{liu2023goat}. Given the immense cost of deploying modern neural networks, this raises serious questions about the efficacy of the typical train/test split methodology for evaluating the ability of a model to generalize beyond a training set~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be one in trillions~\cite{iso26262}. Collecting, labelling, and testing a new set of data for every software change-as required by law- would be prohibitively expensive. Therefore, a new evaluation methodology is required. As such, we propose an evaluation metholodgy, centered on the statistical field of survival analysis, which tests a model against `worst-case' input to verify the efficacy of one software or hardware decision over another. Then, we use this method to examine and minimize the deployment cost for a singular model architecture, measuring this in terms of both power and monetary cost. In short, our goal is to answer three questions.

\subsection{Research Questions}
Our goal is to answer three questions.
\begin{itemize}
    \item What is relationship between latency, robustness, and deployment cost?
    \item What is the cheapest way to guarantee a certain response time and accuracy?
    \item Does better hardware make better models?
\end{itemize}

@@

\subsection{Contributions}
\begin{itemize}
    \item We confirm previous work about the efficacy adversarial analysis for model selection
    \item We measure the power and monetary cost of deploying a model across three different hardware architectures.
    \item We combine survival analysis with adversarial analysis to build accelerated failure models to compare the effect of model parameter choices.
    \item We use a Tree Parzen Estimator to minimize deployment cost while maximizing accuracy.
    \item Show that smaller models running on smaller hardware is far more cost effective, especially in the context of adversarial robustness.
\end{itemize}

\section{Background}
Machine learning pipelines play a crucial role in the development and deployment of robust and accurate models. However, managing complex pipelines across diverse CPU and GPU architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges. In this paper, we present a comprehensive study on leveraging Kubernetes ~\cite{k8s} for managing a complex machine learning pipeline. We explore the robustness of the pipeline under adversarial attacks and examine the impact of computational cost on model performance in both benign and adversarial contexts.

@@

Furthermore, ensuring the robustness of machine learning (ML) models against adversarial attacks has become a critical concern \cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}. Adversarial attacks aim to exploit vulnerabilities in models by introducing subtle modifications to data submitted to various stages of the ML pipeline, leading to misclassification or otherwise erroneous outputs. Evaluating the robustness of machine learning models against adversarial attacks is crucial to assess their reliability and performance in real-world scenarios. By subjecting the machine learning pipeline to carefully crafted adversarial inputs, we can measure its resilience and identify potential vulnerabilities.

@@

In this paper, we present a comprehensive study that combines Kubernetes as the underlying infrastructure for managing a complex machine learning pipeline across a variety of CPU and GPU architectures. We can investigate the robustness of the pipeline against adversarial attacks and explore the relationship between computational cost, model loss, and  prediction accuracy in both benign and adversarial contexts. Our experiments and analysis provide valuable insights into the trade-offs and considerations when deploying machine learning models under varying computational constraints and adversarial conditions.

@@

\subsubsection{Failure Rate}
 To encompass the cost of a particular model or attack, we can think of the failure rate as a function of time (\textit{e.g.} training time, inference time, attack generation time, etc.) and some covariates (\textit{e.g.} noise distance, model size, hardware resources) such that:
\[
h(t; \theta) :=  \frac{\mathbb{P}(\textrm{False~Classification})}{\Delta t}
\]
where $\mathbb{P}$ is a probability and $\Delta t$ is a time interval. To get a more precise and reliable estimate of a model's failure characteristics, we can use accelerated failure time models~\cite{meyers_aft} that model the \textbf{survival time}, $S(t)$, as a function of the samples, $x$, the labels, $y$, and some set of covariates, $\theta$ such that:
\[
S(t; x,y, \theta) := 1 - \int_{t=0}^{\infty} h(t;\theta) d \theta
\]

\subsection{AFR models}
\label{afr}
Accelerated failure rate models are statistical models used to analyze multivariate effects on the observed failure rate to predict the expected survival time ($\mathbb{E}[S(t; x,y, \theta)]$) across a wide variety of circumstances~\cite{aft_models,meyers_aft}. However, this requires a choice in modelling distribution for $S$. We tested Log-Logistic, Log-Normal, and Weibull distributions, relying on AIC, BIC, and Concordance to choose the best-fit, following the best-practices of other research~\cite{aft_models,meyers_aft}.  This analysis allows us to test the model under extreme perturbations, revealing not only the accuracy under ideal test scenarios, but to see the model's performance in the presence of noise that's designed to be adversarial. However, we still have to find optimal configurations for both the attack and defence, which often rely on parameters drawn from continuous or infinite spaces. In order to minimize the cost of evaluationm, we must be clever about how we search.

@@

\subsection{}

>>>>

\title{Towards Reliable Machine Learning Deployments in the Cloud}
% \thanks{Identify applicable funding agency here. If none, delete this.}
\author{\IEEEauthorblockN{1\textsuperscript{st} Charles Meyers}
\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
cmeyers@cs.umu.se}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Mohammad Reza}
\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
fake@fake.se}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Tommy Löfstedt}
\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
tommy@cs.umu.se}
\and
\IEEEauthorblockN{4\textsuperscript{th} Erik Elmroth}
\IEEEauthorblockA{\textit{Dept. of Computing Science} \\
\textit{Umeå University}\\
Umeå, Sweden \\
elmroth@cs.umu.se}
}

@@

\begin{abstract}
Considering the growing prominence of production-level AI and the threat of adversarial attacks that can poison a machine learning model against a certain label, evade classification, or reveal sensitive data about the model and training data to an attacker, adversaries pose fundamental problems to machine learning systems. Prior research has noted the need to extend beyond the normal train-test split paradigm for evaluating models due of the ease with which one can generally find adversarial counterexamples. Additionally, testing model changes likely means deploying the models to a car, medical imaging device, or drone to see how it affects performance, making un-tested changes a public problem. Furthermore, the relationship between model learning rate, batch size, training time, convergence time, and deployment cost is highly complex. So, instead of this train-test split methodology, we propose using accelerated failure time models to measure the effect of hardware choice, batch size, number of epochs, and learning rate by using adversarial attacks to induce failures on a reference model architecture. We evaluate several GPU types and use the Tree Parzen Estimator to maximize model robustness and minimize model run-time simultaneously. In this way, we can evaluate the model and optimize it in a single step, which provides a precise way to not only measure the effect of different hardware deployments but also of the model parameters. Using this technique, we demonstrate that newer, more-powerful hardware does decrease the training time, but with a monetary and power cost that far outpaces the marginal gains in accuracy.
\end{abstract}

@@

\section{Introduction}
\subsection{Motivations}
% \begin{itemize}
%     % \item \textbf{BIG} Data is the trend
%     % \item Costs are astronomical
%     \item Prevailing regulatory framework is clear about the robustness requirements, documented software changes, and explainable processes.
%     \item Other work relies on unreliable test/train split methodology
%     \item Which means that cars, medical equipment is tested in the wild
% \end{itemize}

Recently, machine learning using neural networks has become a popular way to classify large amounts of data---with applications ranging from medical imaging~\cite{ai_medical_imaging} to aviation~\cite{ai_aviation} and from security~\cite{ai_security,ai_luggage,ai_prison} to self-driving cars~\cite{ai_automotive}. However, neural networks need large amounts of data\cite{desislavov2021compute,bailly2022effects} to train ever-larger model~\cite{desislavov2021compute}, yielding increasingly marginal gains on test-set accuracy~\cite{sun2017revisiting}. Furthermore, popular models like Generative Pre-trained Transformer (GPT)\cite{floridi2020gpt} or ResNet~\cite{resnet} have many millions of parameters, requiring equally large training datasets. Media reports place the cost of training a large language model somewhere between 4 and 63 million dollars~\cite{}, meaning only a few entities in the whole world have the requisite hardware and/or cloud budget to build a competing system. Facebook's large language model, dubbed LLaMA, was placed on the codesharing website, GitHub~\cite{llama}. Immediately, an open-sourced clone was created, which itself spawned hundreds of offshoot projects~\cite{openllama}. The newest version of this open-source large language model (LLM) is able to outperform the commercially available GPT-3.5 model with a fraction of the parameters (13 Billion), small enough to run on a laptop without a graphics processing unit (GPU)~\cite{liu2023goat}. Given the immense cost of deploying modern neural networks, the required number of test samples creates serious questions about the efficacy of the typical train/test split methodology for evaluating the ability of a model to generalize beyond a training set~\cite{meyers} since regulatory standards around safety-critical software applications~\cite{IEC61508,iso26262,aviation_software,safetyframework} clearly define the maximum failure rate to be between $[1e-12, 1e-15]$ depending on the number of lives at risk ~\cite{iso26262}. Collecting, labelling, and testing a new set of data for every software change-as required by law would be prohibitively expensive. Therefore, a new evaluation methodology is required. As such, we propose an evaluation metholodgy, centered around survival analysis, which tests a model against `worst-case' input to verify the efficacy of one of modelling deployment decision over another. Then, we use this method to examine and minimize the deployment cost for a singule model architecture, measuring this in terms of both power and monetary cost. In short, our goal is to answer three questions,

\subsection{Research Questions}
Our goal is to answer the following three questions:
\begin{itemize}
    \item What is the relationship between latency, robustness, and deployment cost?
    \item What is the cheapest way to guarantee a certain response time and accuracy?
    \item Does better hardware lead to better models?
\end{itemize}

@@

\subsection{Contributions}
\begin{itemize}
    \item We confirm previous work about the efficacy of adversarial analysis for model selection.
    \item We measure the power and monetary cost of deploying a model across three different hardware architectures.
    \item We combine survival analysis with adversarial analysis to build accelerated failure models to compare the effect of model parameter choices.
    \item We use a Tree Parzen Estimator to minimize deployment cost while maximizing accuracy.
    \item Show that smaller models running on smaller hardware is far more cost effective, especially in the context of adversarial robustness.
\end{itemize}

\section{Background}
Machine learning pipelines play a crucial role in the development and deployment of robust and accurate models. However, managing complex pipelines across diverse CPU and GPU architectures, ensuring robustness against adversarial attacks, and understanding the relationship between computational cost, model loss, and prediction accuracy remain ongoing challenges. In this paper, we present a comprehensive study on leveraging Kubernetes~\cite{k8s} to manage a complex machine learning pipeline. We explore the robustness of the pipeline under adversarial attacks and examine the impact of computational cost on model performance in both benign and adversarial contexts.

@@

Furthermore, ensuring the robustness of machine learning  models against adversarial attacks has become a critical concern~\cite{adversarialpatch, carlini_towards_2017, croce_reliable_2020, hopskipjump, chakraborty2018adversarial, art2018}. Adversarial attacks aim to exploit vulnerabilities in models by introducing subtle modifications to data submitted to various stages of the ML pipeline, leading to misclassification or otherwise erroneous outputs. Evaluating the robustness of ML models against adversarial attacks is crucial to assess their reliability and performance in real-world scenarios. By subjecting the ML pipeline to carefully crafted adversarial inputs, we can measure its resilience and identify potential vulnerabilities.

@@

In this paper, we present a comprehensive study that combines Kubernetes as the underlying infrastructure for managing a complex ML pipeline across a variety of CPU and GPU architectures. We can investigate the robustness of the pipeline against adversarial attacks and explore the relationship between computational cost, model loss, and  prediction accuracy in both benign and adversarial contexts. Our experiments and analysis provide valuable insights into the trade-offs and considerations when deploying machine learning models under varying computational constraints and adversarial conditions.

@@

\subsubsection{Failure Rate}
 To encompass the cost of a particular model or attack, we can think of the failure rate as a function of time (\textit{e.g.} training time, inference time, attack generation time, etc.) and some covariates (\textit{e.g.} noise distance, model size, hardware resources) such that:
\[
h(t; \theta) :=  \frac{\mathbb{P}(\textrm{False~Classification})}{\Delta t}
\]
where $\mathbb{P}$ is a probability and $\Delta t$ is a time interval. To get a more precise and reliable estimate of a model's failure characteristics, we can use accelerated failure time models that model the \textbf{survival time}, $S(t)$, as a function of the samples, $x$, the labels, $y$, and some set of covariates, $\theta$ such that:
\[
S(t; x,y, \theta) := 1 - \int_{t=0}^{\infty} h(t;\theta) d \theta
\]

\subsection{AFR models}
\label{afr}
Accelerated failure rate models are statistical models used to analyze multivariate effects on the observed failure rate to predict the expected survival time ($\mathbb{E}[S(t; x,y, \theta)]$) across a wide variety of circumstances~\cite{aft_models,kleinbaum1996survival}. However, this requires a choice in modelling distribution for $S$. We tested Log-Logistic, Log-Normal, and Weibull distributions, relying on Akaike Information Criterion (AIC), Bayesian Information Criteria (BIC), and Concordance to choose the best-fit, following the best-practices of other research~\cite{aft_models}.  This analysis allows us to test the model under extreme perturbations, revealing not only the accuracy under ideal test scenarios, but to see the model's performance in the presence of noise that's designed to be adversarial. However, we still have to find optimal configurations for both the attack and defence, which often rely on parameters drawn from continuous or infinite spaces. In order to minimize the cost of evaluation, we must be clever about how we search.

@@

\subsection{Survival Time}
\input{plots/combined/aft_comparison}
